Modal Abstractions for Virtualizing Memory Addresses

### 2025-03-23 examples.tex
pass through 5.3

The wrinkle, and the importance of the modal treatment of assertions, is that the target thread's precondition is \emph{relative to its address space}, 
not the address space of the calling thread shown as 
$[\rtv'](\mathcal{I}\texttt{ASpace}(\theta,\Xi,m) \ast \texttt{Pother})$
in the specfication. 
The precondition of this code,
in context, would include that the initial stack pointer (before \lstinline|rsp| is updated)
has a return address expecting the then-current callee-save register values and 
suitably updated (i.e., post-return) stack in the \emph{current} (initial) address space;
this would be part of \textsf{P} in the precondition.
The specification also requires that
the stack pointer saved in the context to restore expects the same of the saved registers and stack 
\emph{in the other address space}. 
The other-space modality plays a critical role here; \textsf{Pother} would contain these assumptions in the other
address space.

@@

>>>>

The wrinkle, and the importance of the modal treatment of assertions, is that the target thread's precondition is \emph{relative to its address space}, 
not the address space of the calling thread, which is reflected by
the other-space modality 
$[\rtv'](\mathcal{I}\texttt{ASpace}(\theta,\Xi,m) \ast \texttt{Pother})$
in the specfication. 
The precondition of this code,
in context, would include that the initial stack pointer (before \lstinline|rsp| is updated)
has a return address expecting the then-current callee-save register values and 
suitably updated (i.e., post-return) stack in the \emph{current} (initial) address space;
this would be part of \textsf{P} in the precondition.
The specification also requires that
the stack pointer saved in the context to restore expects the same of the saved registers and stack 
\emph{in the other address space}. 
The other-space modality plays a critical role here; \textsf{Pother} would contain these assumptions in the other
address space.
\looseness=-1

@@

While prior work has verified context switches within a single address space~\cite{ni2007contexts}, and context switches
without any code before or after~\cite{syeda2020formal} (i.e., not reasoning about the impact of address space change
on what data was accessible), this is the first verification handling both.
